---
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
author: "Kristy Robledo"
title: "Statistical report"
output: 
  officedown::rdocx_document:
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: 0.5
      footer: 0.5
      gutter: 0
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(gtsummary)
library(tidyverse)
library(palmerpenguins)
library(flextable)

```

## tbl_summary

```{r, tab.id = "tab1"}


# create a table
penguins |>
  select(species, sex, bill_length_mm, bill_depth_mm, flipper_length_mm) |>
  tbl_summary(by = sex, 
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{N_nonmiss}", "{mean}  ({sd})", "{min}-{max}")), 
              label = list(
                species ~ "Species",
                bill_length_mm ~ "Bill Length (mm)"
              )) |>
  add_overall() |>
  add_p() ->tbl_base

tbl_base |>
  as_flex_table() |>
  set_caption("Summary statistics for penguins dataset")
```

In the females, there are `r inline_text(tbl_base, variable ="species", level="Adelie", column="female")` Adelie species, and overall there are `r inline_text(tbl_base, variable ="species", level="Adelie", column="stat_0")`, 

## tbl_regression

```{r, tab.id="tab1"}
lm(bill_length_mm~ species+sex+flipper_length_mm, data = penguins) |>
  tbl_regression() |>
  add_global_p() |>
  as_flex_table() |>
  set_caption("Regression model for bill length")

```

## tbl_stack tbl_merge

```{r, tab.id="tab2"}
penguins |>
  select(species, sex, bill_length_mm, bill_depth_mm, flipper_length_mm) |>
  tbl_summary(by = sex, 
              type = list(all_continuous() ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{N_nonmiss}", "{mean}  ({sd})", "{min}-{max}")), 
              label = list(
                species ~ "Species",
                bill_length_mm ~ "Bill Length (mm)"
              ))  ->tbl_1

lm(bill_length_mm~ species+sex+flipper_length_mm, data = penguins) |>
  tbl_regression(, 
              labels = list(
                species ~ "Species",
                bill_length_mm ~ "Bill Length (mm)"
              )) |>
  add_global_p()->tbl_lm

tbl_merge(list(tbl_1, tbl_lm), 
          tab_spanner = c("**Summary statistics**", "**Regression model**")) |>
  as_flex_table() |>
  set_caption("Summary statistics and regression model for penguins dataset")
```

Males are on average `r inline_text(tbl_lm, variable = sex, level = "male", pattern = "{estimate} mm (95% CI: {conf.low}- {conf.high}mm)")` larger in bill length compared to females (`r inline_text(tbl_lm, variable = sex, pattern = "{p.value}")`). 

```{r}
?tbl_uvregression
```

